<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Example: Hierarchical Models}
-->
An example using the fitness model
==================================

This document describe a toy example for the use of the package systemicrisk.

```{r}
library(systemicrisk)
```
Suppose we observe the following vector of total liabilities and todal assets.
```{r}
l <- c(714,745,246, 51,847)
a <- c(872, 412, 65, 46,1208)
```

The following sets up a model for 5 banks:
```{r}
mod <- Model.additivelink.exponential.fitness(n=5,alpha=-2.5,beta=0.3,gamma=1.0,
                 lambdaprior=Model.fitness.genlambdaparprior(ratescale=500))
```

Choosing thinning to ensure sample is equivalent to number of 
```{r}
thin <- choosethin(l=l,a=a,model=mod,silent=TRUE)
thin
```
Running the sampler to produce 1000 samples.
```{r}
res <- sample_HierarchicalModel(l=l,a=a,model=mod,nsamples=1e3,thin=thin,silent=TRUE)
```
Some examples of the matrics generated are below.
```{r}
res$L[[1]]
res$L[[2]]
```

The sampler produces samples from the conditional distribution of
matrix and parameter values given the observed data.
To see the posterior distribution of the liabilities of Bank 1 towards Bank 2:
```{r fig.width=7,fig.height=4}
plot(ecdf(sapply(res$L,function(x)x[1,2])))
```



Diagnostic of the R-output
--------------------------

All the caveats of MCMC algorithms apply. In particular the samples are dependent. 

Some automatic diagnostic can be generated via the function diagnose.
```{r}
diagnose(res)
```
Trace plots  of individual liabilities also shoud show rapid mixing - as seems to be the case for the  liabilities of Bank 1 towards Bank 2.

```{r fig.width=7,fig.height=4}
plot(sapply(res$L,function(x)x[1,2]),type="b")
```
Trace plot of the fitness of bank 1.
```{r fig.width=7,fig.height=4}
plot(res$theta[1,],type="b")
```

Also, the autocorrelation function should decline quickly. Again, considering the liabilities between bank 1 and bank 2:
```{r fig.width=7,fig.height=4}
acf(sapply(res$L,function(x)x[1,2]))
```

In this case it decays quickly below the white-noise threshold (the
horizontal dashed lines).

